%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Bhavya Wadhwa} % Your Name
\newcommand{\course}{Computer Science} % Your Program
\newcommand{\phone}{413-210-0334} % Your Phone Number
\newcommand{\emaila}{bwadhwa@umass.edu} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +1-\phone}\\
 & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  Bachelor of Science & \href{https://github.com/bhavya6828}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}} \\  
  {UMass Amherst} & \href{www.linkedin.com/in/bhavya-wadhwa-bms/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
\end{tabularx}
}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Science in Computer Science}{GPA: 4.0}
      {University of Massachusetts Amherst, MA}{2024-28}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}



%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Management Intern}{Faridabad, India}
      {Delta Healthcare}{May - July 2024}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Utilized Python (Pandas, Numpy) to clean, organize, and process large CSV datasets related to pharmaceutical inventory, sales, amd order records.}
    \item {Automated routine data tasks such as mergig, filtering, and deduplicating CSV files, improving team efficiency and reducing manual errors.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
    
    \resumeSubheading
      {Undergraduate Research Assisstant}{Amherst, MA}
      {Wireless and Sensor Systems Lab}{May 2025 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Analyzed physiological sensor data (Phybrata) by processing large CSV datasets in Python using Pandas, Numpy, and Matplotlib, focusing on treatment effects across Eyes Open (EO) and Eyes Closed (EC) conditions. }
    \item {Built and evaluated multiple machine learning models (e.g., SVM, Random Forest, KNN, CNN) to classify and detect trends in sensor data related to treatment response.}
    \item {Reviewed and summarized relevant research papers to guide model selection and interpret phsiological patterns and contribute to future poster development.}
    \resumeItemListEnd

     \vspace{-3.0mm}
    
    \resumeSubheading
      {Game Analyst Intern}{Remote}
      {Global Origin, LLC}{June 2025 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Analyzed player data to evaluate game performance, retention, and monetization using Python.}
    \item {Tracked key KPIs including DAU, MAU, ARPU, and churn rate to support data-driven decision-making.}
    \item {Conducted A/B tests and behavioral analysis to optimize game mechanics and user experience.}
    \item {Created visual reports and dashboards to present trends to developers, designers, and marketing teams.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
      
  \resumeSubHeadingListEnd
\vspace{-5.5mm}



%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
    \resumeProject
      {Personal Portfolio Website} %Project Name
      {A fully responsive portfolio to showcase projects and my background.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Designed and developed a fully responsive personal portfolio to showcase projects, experiences, and skills using Next.js for fast routing and optimized performance.}
        \item {Focused on accessibility and performance, resulting in a mobile-friendly, fast-loading site deployed for a global audience.}
        \item {Technology Used: Next.js, Tailwind CSS, Framer Motion}
    \resumeItemListEnd
    \vspace{-2mm}
    
    \resumeProject
      {Realtime Chat App} %Project Name
      {A react based web application which allow users to chat in real time. } %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Used Firebase Authentication(SDK) to facilitate authentication \& Cloud Firestore to store data.}
        \item {Technology Used: Reactjs, Firebase, Bootstrap, HTML.}
    \resumeItemListEnd
    \vspace{-2mm}

    \resumeProject
      {News Aggregator Website} %Project Name
      {A dynamic news website to fetch and display real-time news articles.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Developed a functional news website using Node.js to serve static frontend files and handle backend API requests}
        \item {Integrated the NewsAPI to fetch real-time news articles based on user queries, using Axios for HTTP requests.}
        \item {Technology Used : HTML, CSS, JavaScript, Node.js, Axios, NewsAPI.}
    \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-8.5mm}



%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, Javascript, HTML+CSS } \\
     \textbf{Libraries }{:Pandas, NumPy, Matplotlib, Scikit-learn, Framer Motion }\\ 
     \textbf{Web Dev Tools}{: Nodejs, VScode, Git, Github } \\ 
     \textbf{Frameworks}{: Next.js Tailwind } \\  
      \textbf{Relevent Coursework}{: Data Structures \& Algorithms, Object Oriented Programming, Multivariable Calculus } \\ 
     \textbf{Areas of Interest}{: Web Design and Development, Machine Learning, Cybersecurity, Robotics.} \\
     \textbf{Soft Skills}{: Problem Solving, Self-learning, Presentation, Adaptability} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
